

Penelope felt a chill run through her body as she noticed the sky had grown dark. The sun had disappeared and the horizon was riddled with menacing storm clouds. A strong wind had picked up, blowing the trees and grass about wildly. Penelope began to worry, she had been out too long and now was facing a fierce storm. 

Suddenly, the wind grew stronger, and with it the storm clouds began to take shape. Penelope gasped as she saw the clouds form a lumberjack – the physical manifestation of the timber mill's threat. Penelope stared in awe, as its form seemed to grow even bigger, with each gust of wind.

It was then that Penelope remembered the wise old kangaroo's words – that she must trust her newfound powers and seek shelter when the storm came. She knew she had to take action. Taking a deep breath, Penelope closed her eyes and focused on the wise old kangaroo. Instantly, a feeling of warmth washed over her – the kangaroo's presence was with her.

Penelope began to walk forward, the wind whipping around her as she trudged through the grass. She kept her eyes focused on the kangaroo's presence, and her feet moved of its own accord. It didn't seem long before she arrived at a great old oak tree, and she knew this was the shelter the wise old kangaroo had summoned her to.

As she stepped under the tree, Penelope felt a warmth blanket her body, shielding her from the storm. She looked up and saw the lumberjack dissipating into the sky, as if it had never been there in the first place. Penelope felt relieved – she had made it in time, and was safe from the storm.

But most of all, Penelope felt grateful for the powers she had been blessed with, and for the wise old kangaroo's guidance. She smiled to herself, and looked up into the sky. The storm had passed, and the sun had begun to peek through the clouds. Penelope knew she had been saved, and she was sure that with the help of her newfound powers, she would be able to protect her family's home from the encroaching timber mill.